They're Clutching up! Team Momentum in Round-Based Esports

### 2022-08-13 paper/paper.qmd
render a plot without error
more on the intro to the paper

[^2]:
    -   The bomb can be picked up by any member of the offensive team.
    -   The bomb carrier is not obstructed at all by carrying the bomb (i.e. movement is the same, weapon usage is the same).
    -   The defense does not get any visual indication for who is carrying the bomb.
    -   A bomb plant takes five seconds. The timer resets if the player stops planting site prior to completing it.
    -   A bomb defuse takes seven seconds. The timer resets if the player "drops" the bomb.
    -   The bomb takes 45 seconds to defuse after being planted.

@@

CoD has roughly gone through three eras of professional gaming: (1) Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World League (CWL), initiated in 2016; and (3) the 12-franchise CoD League (CDL), running since 2020 and completing three year-long "seasons" completed as of August 2022.[^4] The data set consists of all SnD matches played in tournaments and qualifiers during the CDL era, totaling `r scales::comma(cod_n_series)` series played, in which there were `r scales::comma(cod_n_rounds)` rounds played. Data was collected in spreadsheets by community member "IOUTurtle".[^5]

@@

There have been only a handful of studies of the distribution of games played in a series, most of which assume a constant probability $p$ of a given team winning a game in the series, regardless of the series state. Observing that the American League had dominated the National League in Major League Baseball's (MLB) World Series matchups, implying that matchups should not modeled with $p=0.5$, [@mosteller1952] proposed three approaches for identifying the optimal constant probability value of the stronger team in the World Series, finding $p \approx 0.65$ in each case: (1) a "method of moments", an approach that solves for $p$ from the empirical average number of games won by the loser of the series; (2) maximum likelihood, and (3) maximum chi-square approach. [@chance2020] re-examines the constant probability notion in Major League Baseball's World Series (1923--2018), the National Basketball Association's Finals (1951--2018), and the National Hockey League's Stanley Cup (1939--2018). Chance applies Mosteller's method 1 and 2 and finds strong evidence against the null hypothesis of $p = 0.5$ in the MLB and NHL championship series. Chance outlines a conditional probability framework (likelihood of winning a game given the series state) which can exactly explain the distribution of the number of games played.

Momentum is one of the most frequently published topics in sports analytics. We often use use "streaks" and momentum interchangeably, but as [@steeger2021] note, momentum implies dependence between events, whereas streaking does not. (sentence about negative recency, hinting at "hot hand"... [@miller2018] debunking findings from [@gilovich1985])

Despite the plethora of existing research on games played and momentum in sports, these topics have yet to be investigated heavily in esports. Work has been done to examine in-round win probability in other FPS titles such as Counter-Strike ([@xenopoulos2022]) and Valorant ([@derover2021]), both of which are round-based like CoD SnD. However, research on round-level trends is sparse, perhaps because games like Counter-Strike and Valorant both have economic aspects that can create clear advantages on side in a given round, given how prior rounds played out.[^6]

[^6]: Additionally, both Counter-Strike and Valorant have overtime rules and blocked offensive/defensive roles (i.e. playing either offense or defense for many consecutive rounds).

@@

The empirical offensive round win percentage across all rounds is `r scales::percent(cod_o_win_prop, accuracy = 0.1)`.[^7] @fig-cod-o-round-win-prop shows that offensive round win rate is not quite constant, although, on average, never veers more than 10% from this global average.

[^7]: Offensive round win percentage has been nearly constant across the three games during the CDL era: MW (2020) `r pull_cod_o_win_prop_by_game('MW (2020)')`, Cold War (2021) `r pull_cod_o_win_prop_by_game('Cold War (2021)')`, Vanguard (2022) `r pull_cod_o_win_prop_by_game('Vanguard (2022)')`

::: {#fig-cod-o-round-win-prop}
![](images/cod_o_round_win_prop.png){fig-align="center"}

Offensive round win percentage by series state
:::

>>>>

[^2]: Merchanics regarding the bomb:

    -   The bomb can be picked up by any member of the offensive team.
    -   The bomb carrier is not obstructed at all by carrying the bomb (i.e. movement is the same, weapon usage is the same).
    -   The defense does not get any visual indication for who is carrying the bomb.
    -   A bomb plant takes five seconds. The timer resets if the player stops planting site prior to completing it.
    -   A bomb defuse takes seven seconds. The timer resets if the player "drops" the bomb.
    -   The bomb takes 45 seconds to defuse after being planted.

@@

CoD has roughly gone through three eras of professional gaming: (1) Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World League (CWL), initiated in 2016; and (3) the 12-franchise CoD League (CDL), running since 2020 and completing three year-long "seasons" completed as of August 2022.[^4] The data set consists of all SnD matches played in tournaments and qualifiers during the CDL era, totaling `r scales::comma(cod_n_rounds)` rounds across `r scales::comma(cod_n_series)` series. Data was collected in spreadsheets by community member "IOUTurtle".[^5]

@@

There have been only a handful of studies of the distribution of games played in a series, most of which assume a constant probability $p$ of a given team winning a game in the series, regardless of the series state. [@mosteller1952] observed that the American League had dominated the National League in Major League Baseball's (MLB) World Series matchups, implying that matchups should not modeled with \$p=0.5\$.. Mosteller proposed three approaches for identifying the optimal constant probability value of the stronger team in the World Series, finding \$p \\approx 0.65\$. in each case: (1) a "method of moments", an approach that solves for \$p\$. from the empirical average number of games won by the loser of the series; (2) maximum likelihood, and (3) maximum chi-square approach.

[@chance2020] re-examines the constant probability notion in Major League Baseball's World Series (1923--2018), the National Basketball Association's Finals (1951--2018), and the National Hockey League's Stanley Cup (1939--2018). Chance applies finds strong evidence against the null hypothesis of $p = 0.5$ in the MLB and NHL championship series when applying Mosteller's first and second methods.[^6] Chance's work is closely related to ours and, in fact, provides a guide for the first part of our investigation.

[^6]: Chance goes on to outline a conditional probability framework (likelihood of winning a game given the series state) which can exactly explain the distribution of the number of games played.

Momentum, one of most discussed topics in sports analytics, goes hand-in-hand with a discussion of the nature of series outcomes.[^7] Two opposing fallacies are observed in the context of momentum: the "gambler's fallacy" (negative recency) and "hot hand fallacy" (positive recency). Per \[@ayton2004\], negative recency is "the belief that, for random events, runs of a particular outcome ... will be balanced by a tendency for the opposite outcome", while positive recency is the expectation of observing future results that match recent results.

[^7]: We often use use "streaks" and momentum interchangeably, but as [@steeger2021] note, momentum implies dependence between events, whereas streaking does not.

Studying both player streaks and team streaks in basketball, in both observational and controlled settings. [@gilovich1985] do not find evidence for the hot hand phenomenon. Recently , [@miller2018] refute [@gilovich1985]'s conclusions, finding mathematical evidence that seems to support negative recency. Specifically, they find that a "bias exists in a common measure of the conditional dependence of present outcomes on streaks of past outcomes in sequential data" (streak selection bias) that imply that, under i.i.d. conditions, "the proportion of successes among the outcomes that immediately follow a streak of consecutive successes is expected to be strictly less than the underlying (conditional) probability of success". We agree with Miller's findings, accounting for the streak selection bias in our study of momentum.

Despite the plethora of existing research on games played in a series and momentum in sports, these topics have yet to be investigated heavily in esports. Work has been done to examine in-round win probability in other FPS titles such as Counter-Strike ([@xenopoulos2022]) and Valorant ([@derover2021]), both of which are round-based like CoD SnD. However, research on round-level trends is sparse, perhaps because games like Counter-Strike and Valorant both have economic aspects that can create clear advantages on side in a given round, given how prior rounds played out.[^8]

[^8]: Additionally, both Counter-Strike and Valorant have overtime rules and blocked offensive/defensive roles (i.e. playing either offense or defense for many consecutive rounds).

@@

First, we investigate the constant probability assumption and the distribution of rounds played in a series. Afterwards, we investigate momentum, building on our learnings from the constant probability assumption analysis.

## Distribution of rounds played

The general formula for the probability $P(i)$ that a best-of-$s$ series lasts $i$ rounds given constant probability $p$ of one team[^9] winning each round is

[^9]: If $p > 0.5$, then we might say that this team is the better team (presumably known in hindsight)

$$
s_1 = \frac{s - 1}{2}, s_2 = \frac{s + 1}{2}
$$
$$
P(i) = \frac{(i - 1)!}{s_1!(i - s_2)!}(p^{s_2}(1 - p)^{i - s_2} + p^{i - s_2}(1 - p)^{s_2})
$$

resulting in @tbl-prob-series-lasting-i-rounds} for $s = 11$ and the naive assumption that $p = 0.5$.

| Number of rounds ($i$) | $P(i)$ |
|-----------------------:|-------:|
|                      6 |   3.1% |
|                      7 |   9.4% |
|                      8 |  16.4% |
|                      9 |  21.9% |
|                     10 |  24.6% |
|                     11 |  24.6% |

: The probabilities that a best-of-11 series lasts $i$ rounds ($Pr(i)$, where $i = {6, 7, 8, 9, 10, 11}$) under the assumption that each team has a 50% probability ($p = 0.5$) of winning each game {#tbl-prob-series-lasting-i-rounds}

The empirical offensive round win percentage across all rounds is `r scales::percent(cod_o_win_prop, accuracy = 0.1)`.[^10] @fig-cod-o-round-win-prop shows that offensive round win rate is not quite constant, although never veers more than 10% from this global average.

[^10]: Offensive round win percentage has been nearly constant across the three games during the CDL era: MW (2020) `r pull_cod_o_win_prop_by_game('MW (2020)')`, Cold War (2021) `r pull_cod_o_win_prop_by_game('Cold War (2021)')`, Vanguard (2022) `r pull_cod_o_win_prop_by_game('Vanguard (2022)')`

![Offensive round win percentage by series state](images/cod_o_round_win_prop.png){#fig-cod-o-round-win-prop fig-align="center"}

### 2022-08-13 paper/paper.tex
more on the intro to the paper

Finally, I evaluate behavior when teams have two rounds left to win the
series, observing a peak in COD offensive win percentages in the 4-4
state, and no such oddity in Valorant.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, enhanced, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, sharp corners, frame hidden, breakable]}{\end{tcolorbox}}\fi

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  One team eliminates all members of the other team prior to a bomb
  plant. (Eliminating team wins.)
\item
  The offensive team eliminates all members of the defensive team after
  a bomb plant.\footnote{\begin{itemize}
    \tightlist
    \item
      The bomb can be picked up by any member of the offensive team.
    \item
      The bomb carrier is not obstructed at all by carrying the bomb
      (i.e.~movement is the same, weapon usage is the same).
    \item
      The defense does not get any visual indication for who is carrying
      the bomb.
    \item
      A bomb plant takes five seconds. The timer resets if the player
      stops planting site prior to completing it.
    \item
      A bomb defuse takes seven seconds. The timer resets if the player
      ``drops'' the bomb.
    \item
      The bomb takes 45 seconds to defuse after being planted.
    \end{itemize}} (Offense wins.)
\item
  The defensive team defuses the bomb after a bomb plant.\footnote{Often
    the defensive team will try to eliminate all team members prior to
    making the defuse, but in some cases, they may try to ``ninja''
    defuse.} (Defense wins.)
\item
  The offensive team does not make a plant by the time the round timer
  ends. (Defense wins.)
\end{enumerate}

@@

CoD has roughly gone through three eras of professional gaming: (1)
Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World
League (CWL), initiated in 2016; and (3) the 12-franchise CoD League
(CDL), running since 2020 and completing three year-long ``seasons''
completed as of August 2022.\footnote{CoD is fairly unique compared to
  other esports in that it runs on an annual lifecycle (released coming
  in the late fall), where a new game is published every year under the
  same title. Each new game bears resemblance to past ones, often
  introducing relatively small variations (``improvements'') to
  graphics, game modes, and other facets of gameplay. During the CDL
  era, the games released have been Modern Warfare (2020), Cold War
  (2021) and Vanguard (2022).} The data set consists of all SnD matches
played in tournaments and qualifiers during the CDL era, totaling 1,704
series played, in which there were 15,584 rounds played. Data was
collected in spreadsheets by community member ``IOUTurtle''.\footnote{Data:
  https://linktr.ee/CDLArchive. Author: https://twitter.com/IOUTurtle}

@@

There have been only a handful of studies of the distribution of games
played in a series, most of which assume a constant probability \(p\) of
a given team winning a game in the series, regardless of the series
state. Observing that the American League had dominated the National
League in Major League Baseball's (MLB) World Series matchups, implying
that matchups should not modeled with \(p=0.5\), (Mosteller 1952)
proposed three approaches for identifying the optimal constant
probability value of the stronger team in the World Series, finding
\(p \approx 0.65\) in each case: (1) a ``method of moments'', an
approach that solves for \(p\) from the empirical average number of
games won by the loser of the series; (2) maximum likelihood, and (3)
maximum chi-square approach. (Chance 2020) re-examines the constant
probability notion in Major League Baseball's World Series (1923--2018),
the National Basketball Association's Finals (1951--2018), and the
National Hockey League's Stanley Cup (1939--2018). Chance applies
Mosteller's method 1 and 2 and finds strong evidence against the null
hypothesis of \(p = 0.5\) in the MLB and NHL championship series. Chance
outlines a conditional probability framework (likelihood of winning a
game given the series state) which can exactly explain the distribution
of the number of games played.

Momentum is one of the most frequently published topics in sports
analytics. We often use use ``streaks'' and momentum interchangeably,
but as (Steeger, Dulin, and Gonzalez 2021) note, momentum implies
dependence between events, whereas streaking does not. (sentence about
negative recency, hinting at ``hot hand''\ldots{} (Miller and Sanjurjo
2018) debunking findings from (Gilovich, Vallone, and Tversky 1985))

Despite the plethora of existing research on games played and momentum
in sports, these topics have yet to be investigated heavily in esports.
Work has been done to examine in-round win probability in other FPS
titles such as Counter-Strike ((Xenopoulos, Freeman, and Silva 2022))
and Valorant ((DeRover 2021)), both of which are round-based like CoD
SnD. However, research on round-level trends is sparse, perhaps because
games like Counter-Strike and Valorant both have economic aspects that
can create clear advantages on side in a given round, given how prior
rounds played out.\footnote{Additionally, both Counter-Strike and
  Valorant have overtime rules and blocked offensive/defensive roles
  (i.e.~playing either offense or defense for many consecutive rounds).}

@@

The empirical offensive round win percentage across all rounds is
47.8\%.\footnote{Offensive round win percentage has been nearly constant
  across the three games during the CDL era: MW (2020) 47.2\%, Cold War
  (2021) 47.9\%, Vanguard (2022) 48.1\%}
Figure~\ref{fig-cod-o-round-win-prop} shows that offensive round win
rate is not quite constant, although, on average, never veers more than
10\% from this global average.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-chance2020}{}}%
Chance, Don. 2020. {``Conditional Probability and the Length of a
Championship Series in Baseball, Basketball, and Hockey.''}
\emph{Journal of Sports Analytics} 6 (2): 111--27.
\url{https://doi.org/10.3233/JSA-200422}.

>>>>

Finally, I evaluate behavior when teams have two rounds left to win the
series, observing a peak in COD offensive win percentages in the 4-4
state, and no such oddity in Valorant.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, boxrule=0pt, enhanced, borderline west={3pt}{0pt}{shadecolor}, frame hidden, sharp corners, breakable]}{\end{tcolorbox}}\fi

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  One team eliminates all members of the other team prior to a bomb
  plant. (Eliminating team wins.)
\item
  The offensive team eliminates all members of the defensive team after
  a bomb plant.\footnote{Merchanics regarding the bomb:

    \begin{itemize}
    \tightlist
    \item
      The bomb can be picked up by any member of the offensive team.
    \item
      The bomb carrier is not obstructed at all by carrying the bomb
      (i.e.~movement is the same, weapon usage is the same).
    \item
      The defense does not get any visual indication for who is carrying
      the bomb.
    \item
      A bomb plant takes five seconds. The timer resets if the player
      stops planting site prior to completing it.
    \item
      A bomb defuse takes seven seconds. The timer resets if the player
      ``drops'' the bomb.
    \item
      The bomb takes 45 seconds to defuse after being planted.
    \end{itemize}} (Offense wins.)
\item
  The defensive team defuses the bomb after a bomb plant.\footnote{Often
    the defensive team will try to eliminate all team members prior to
    making the defuse, but in some cases, they may try to ``ninja''
    defuse.} (Defense wins.)
\item
  The offensive team does not make a plant by the time the round timer
  ends. (Defense wins.)
\end{enumerate}

@@

CoD has roughly gone through three eras of professional gaming: (1)
Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World
League (CWL), initiated in 2016; and (3) the 12-franchise CoD League
(CDL), running since 2020 and completing three year-long ``seasons''
completed as of August 2022.\footnote{CoD is fairly unique compared to
  other esports in that it runs on an annual lifecycle (released coming
  in the late fall), where a new game is published every year under the
  same title. Each new game bears resemblance to past ones, often
  introducing relatively small variations (``improvements'') to
  graphics, game modes, and other facets of gameplay. During the CDL
  era, the games released have been Modern Warfare (2020), Cold War
  (2021) and Vanguard (2022).} The data set consists of all SnD matches
played in tournaments and qualifiers during the CDL era, totaling 15,584
rounds across 1,704 series. Data was collected in spreadsheets by
community member ``IOUTurtle''.\footnote{Data:
  https://linktr.ee/CDLArchive. Author: https://twitter.com/IOUTurtle}

@@

There have been only a handful of studies of the distribution of games
played in a series, most of which assume a constant probability \(p\) of
a given team winning a game in the series, regardless of the series
state. (Mosteller 1952) observed that the American League had dominated
the National League in Major League Baseball's (MLB) World Series
matchups, implying that matchups should not modeled with \$p=0.5\$..
Mosteller proposed three approaches for identifying the optimal constant
probability value of the stronger team in the World Series, finding \$p
\textbackslash approx 0.65\$. in each case: (1) a ``method of moments'',
an approach that solves for \$p\$. from the empirical average number of
games won by the loser of the series; (2) maximum likelihood, and (3)
maximum chi-square approach.

(Chance 2020) re-examines the constant probability notion in Major
League Baseball's World Series (1923--2018), the National Basketball
Association's Finals (1951--2018), and the National Hockey League's
Stanley Cup (1939--2018). Chance applies finds strong evidence against
the null hypothesis of \(p = 0.5\) in the MLB and NHL championship
series when applying Mosteller's first and second methods.\footnote{Chance
  goes on to outline a conditional probability framework (likelihood of
  winning a game given the series state) which can exactly explain the
  distribution of the number of games played.} Chance's work is closely
related to ours and, in fact, provides a guide for the first part of our
investigation.

Momentum, one of most discussed topics in sports analytics, goes
hand-in-hand with a discussion of the nature of series
outcomes.\footnote{We often use use ``streaks'' and momentum
  interchangeably, but as (Steeger, Dulin, and Gonzalez 2021) note,
  momentum implies dependence between events, whereas streaking does
  not.} Two opposing fallacies are observed in the context of momentum:
the ``gambler's fallacy'' (negative recency) and ``hot hand fallacy''
(positive recency). Per {[}Ayton and Fischer (2004){]}, negative recency
is ``the belief that, for random events, runs of a particular outcome
\ldots{} will be balanced by a tendency for the opposite outcome'',
while positive recency is the expectation of observing future results
that match recent results.

Studying both player streaks and team streaks in basketball, in both
observational and controlled settings. (Gilovich, Vallone, and Tversky
1985) do not find evidence for the hot hand phenomenon. Recently ,
(Miller and Sanjurjo 2018) refute (Gilovich, Vallone, and Tversky
1985)'s conclusions, finding mathematical evidence that seems to support
negative recency. Specifically, they find that a ``bias exists in a
common measure of the conditional dependence of present outcomes on
streaks of past outcomes in sequential data'' (streak selection bias)
that imply that, under i.i.d. conditions, ``the proportion of successes
among the outcomes that immediately follow a streak of consecutive
successes is expected to be strictly less than the underlying
(conditional) probability of success''. We agree with Miller's findings,
accounting for the streak selection bias in our study of momentum.

Despite the plethora of existing research on games played in a series
and momentum in sports, these topics have yet to be investigated heavily
in esports. Work has been done to examine in-round win probability in
other FPS titles such as Counter-Strike ((Xenopoulos, Freeman, and Silva
2022)) and Valorant ((DeRover 2021)), both of which are round-based like
CoD SnD. However, research on round-level trends is sparse, perhaps
because games like Counter-Strike and Valorant both have economic
aspects that can create clear advantages on side in a given round, given
how prior rounds played out.\footnote{Additionally, both Counter-Strike
  and Valorant have overtime rules and blocked offensive/defensive roles
  (i.e.~playing either offense or defense for many consecutive rounds).}

@@

First, we investigate the constant probability assumption and the
distribution of rounds played in a series. Afterwards, we investigate
momentum, building on our learnings from the constant probability
assumption analysis.

\hypertarget{distribution-of-rounds-played}{%
\subsection{Distribution of rounds
played}\label{distribution-of-rounds-played}}

The general formula for the probability \(P(i)\) that a best-of-\(s\)
series lasts \(i\) rounds given constant probability \(p\) of one
team\footnote{If \(p > 0.5\), then we might say that this team is the
  better team (presumably known in hindsight)} winning each round is

\[
s_1 = \frac{s - 1}{2}, s_2 = \frac{s + 1}{2}
\]

\[
P(i) = \frac{(i - 1)!}{s_1!(i - s_2)!}(p^{s_2}(1 - p)^{i - s_2} + p^{i - s_2}(1 - p)^{s_2})
\]

resulting in Table~\ref{tbl-prob-series-lasting-i-rounds}\} for
\(s = 11\) and the naive assumption that \(p = 0.5\).

\hypertarget{tbl-prob-series-lasting-i-rounds}{}
\begin{longtable}[]{@{}rr@{}}
\caption{\label{tbl-prob-series-lasting-i-rounds}The probabilities that
a best-of-11 series lasts \(i\) rounds (\(Pr(i)\), where
\(i = {6, 7, 8, 9, 10, 11}\)) under the assumption that each team has a
50\% probability (\(p = 0.5\)) of winning each game}\tabularnewline
\toprule()
Number of rounds (\(i\)) & \(P(i)\) \\
\midrule()
\endfirsthead
\toprule()
Number of rounds (\(i\)) & \(P(i)\) \\
\midrule()
\endhead
6 & 3.1\% \\
7 & 9.4\% \\
8 & 16.4\% \\
9 & 21.9\% \\
10 & 24.6\% \\
11 & 24.6\% \\
\bottomrule()
\end{longtable}

The empirical offensive round win percentage across all rounds is
47.8\%.\footnote{Offensive round win percentage has been nearly constant
  across the three games during the CDL era: MW (2020) 47.2\%, Cold War
  (2021) 47.9\%, Vanguard (2022) 48.1\%}
Figure~\ref{fig-cod-o-round-win-prop} shows that offensive round win
rate is not quite constant, although never veers more than 10\% from
this global average.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-ayton2004}{}}%
Ayton, Peter, and Ilan Fischer. 2004. {``The Hot Hand Fallacy and the
Gambler{'}s Fallacy: Two Faces of Subjective Randomness?''} \emph{Memory
\& Cognition} 32 (8): 13691378.

\leavevmode\vadjust pre{\hypertarget{ref-chance2020}{}}%
Chance, Don. 2020. {``Conditional Probability and the Length of a
Championship Series in Baseball, Basketball, and Hockey.''}
\emph{Journal of Sports Analytics} 6 (2): 111--27.
\url{https://doi.org/10.3233/JSA-200422}.

### 2022-08-13 presentation.qmd
more on the intro to the paper

all_possible_outcomes <- tibble(
  n_rounds = 6L:11L
) |> 
  mutate(
    x = map_dbl(n_rounds, ~sample(c(0L, 1L), size = .x, replace = TRUE))
  )

@@

plot_series_outcome_prop_over_expected <- function(series_outcome_prop, game) {
  .lvls <- sprintf('6-%d', 0:5)
  .axis_x_text_size <- 14

@@

```{r}
#| label: cod_series_outcomes_chi-eval
#| eval: true
avg_actual_cod_rounds_per_series <- 9.15
avg_expected_cod_rounds_per_series <- 9.29
cod_series_outcomes_chi <- '15.4 (<=0.01)'
```

>>>>

@@

plot_series_outcome_prop_over_expected <- function(series_outcome_prop) {
  .lvls <- sprintf('6-%d', 0:5)
  .axis_x_text_size <- 14

@@

```{r}
#| label: cod_series_outcomes_chi-eval
#| eval: true
avg_actual_cod_rounds_per_series <- 9.15
avg_expected_cod_rounds_per_series <- 9.29
cod_series_outcomes_chi <- '16.0 (<=0.01)'
```
